Equations & R Code

### 2017-03-31 manuscript/coexistence-stability_SI.tex
final edits for R1 submission

  \NormalTok{if(Rsd_annual ==}\StringTok{ }\DecValTok{0}\NormalTok{) \{}
    \NormalTok{Rvector        <-}\StringTok{ }\KeywordTok{rlnorm}\NormalTok{(seasons, Rmu, Rsd_annual)}
  \NormalTok{\}}
  \NormalTok{if(Rsd_annual >}\StringTok{ }\DecValTok{0}\NormalTok{) \{}
    \NormalTok{Rvector        <-}\StringTok{ }\KeywordTok{urlnorm}\NormalTok{(seasons, Rmu, Rsd_annual, }\DataTypeTok{lb =} \DecValTok{0}\NormalTok{, }\DataTypeTok{ub =} \DecValTok{200}\NormalTok{)}
  \NormalTok{\}}

@@

In the main text we constrained our focus to four-species communities
because getting more than four species to coexist by relative
nonlinearity is tricky, and usually requires adding another coexistence
mechanism on top off relative nonlinearity (Yuan \& Chesson 2015). The
storage effect does not suffer from this limitation, but we wanted our
results in the main text to be easily comparable between coexistence
mechanisms. Here, we show that our results are qualitatively similar if
we simulate an eight-species community with species coexistence
maintained by the storage effect. We conducted the same numerical
simulations described in the main text for Figure 2. Quoting from the
main text:

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{./components/SI_storage_effect_eightspp_local_regional.png}
  \caption{Variability of total community biomass as a function of species richness when coexistence is maintained by the storage effect. The left panel shows results from simulations where environmental cue variance determines the number of species that coexist in a community. The right panel shows results from simulations where environmental cue variance is fixed at a level ($\sigma_E^2=10$) that allows coexistence of all eight species, but species are removed to manipulate diversity. The left-hand panel represents a "regional" diversity--ecosystem variability relationship across a natural diversity gradient, whereas the right-hand panel represents a "local" diversity--ecosystem variability relationship. Points are jittered within discrete richness values for visual clarity. Lines show the mean trend (loess fits).}
\end{figure}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Environment-competition covariance (\emph{EC} covariance) becomes less
  positive
\item
  Environemntal variation decreases
\item
  Buffering of population growth rate declines
\end{enumerate}

@@

Our results are qualitatively similar: (1) increasing environmental
variation allows more species to coexist, creating a positive
relationship between species richness and ecosystem variability
(richness increases along x-axes within panels); (2) and at any given
level of environmental variability, it is always better to have more
species, creating a within-site negative relationship between species
richness and ecosystem variability (Fig. SI-2). Although the qualitative
patterns are similar, increasing the dormant mortality rate has two
interesting effects: (1) it makes coexistence more difficult, (2) it
reduces the absolute value of ecosystem \emph{CV} by reducing mean
population size a little bit and by reducing the temporal standard
deviation a lot, and (3) it weakens the buffering effect of additional
species (compare the spread of the lines between top and bottom panels
of Fig. SI-2). The second result occurs because population fluctuations
are reduced when very little biomass can be activated to the live stage
at the beginning of each season. That is, in terms of an annual plant,
germination of live biomass is always a fraction of a very small number.
The third result is a consequence of the second: populations are not
fluctuating that much, so total \emph{CV} can only be reduced by so much
with the addition of another species.

@@

Condition 1 is already included in our main analysis (Figures 2 and 4 in
the main text). Condition 2 simply creates conditions where some species
cannot coexist, which would not change the relationship between species
richness and ecosystem variability, but rather disallow it. Condition 3
is more interesting, because it could create situations where species
may not coexist, but it could also weaken the diversity--ecosystem
variabilty relationship be reducing mean biomass and the effect of
species with very nonlinear growth rates. To explore the effect of
condition 3, we ran simulations across a gradient of resource
variability (11 levels) crossed with a gradient of mean resource levels
(4 levels: \(\mu_R = 1,2,3,4\)).

As expected, lower mean levels of resource make coexistence more
difficult because resource acquisitive species are never favored (Fig.
SI-3). Our general conclusion remains, however, that positive
diversity--ecosystem variability relationships are possible. However,
the occurence a of positive diversity--ecosystem variability
relationship depends on amount of resource variability being sampled
over and the traits of individual species (e.g., resource uptake
curves). In other words, the patterns we report in the main text require
that fluctuation-dependent species coexistence be possible given the
environmental conditions and species' traits.

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{./components/SI_relative_nonlinearity_four_rmus.png}
  \caption{The effect of environmental variability on ecosystem variability when species coexist via relative nonlinearity. The species pool increases from one to four species, with the fourth species being most unstable (e.g., resource conservative to resource acquisitive). Increasing environmental variability (the SD of annual resource availability) allows for greater species richness, but species additions do not modulate the effect of environmental variability on ecosystem variability. Higher values of mean resource availability (left to right across panels) makes coexistence easier. Parameter values are as in Figure 2C in the main text.}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=5in]{./components/SI_storage_effect_two_rmus_fourSpeciesOnly.png}
  \caption{Ecosystem \emph{CV} of a four-species community coexisting via the storage effect as a function of environmental cue variance at two levels of mean resource availability (\texttt{Rmu} across tops of panels) and two levels of correlation of species' responses to environmental conditions ($\rho$). Here we simualted community dynamics across a greater range of environmental cue variance (up to 10) to show that the \emph{CV} of four-species communities does not remain flat as environmental variance increases beyond levels shown in the main text. The mean resource level has no effect on the results.}
\end{figure}

>>>>

  \NormalTok{if(Rsd_annual ==}\StringTok{ }\DecValTok{0}\NormalTok{) \{ }\CommentTok{# urlnorm can't handle zero variance}
    \NormalTok{Rvector        <-}\StringTok{ }\KeywordTok{rlnorm}\NormalTok{(seasons, Rmu, Rsd_annual)}
  \NormalTok{\}}
  \NormalTok{if(Rsd_annual >}\StringTok{ }\DecValTok{0}\NormalTok{) \{ }\CommentTok{# when variance greater than zero}
    \NormalTok{Rvector        <-}\StringTok{ }\KeywordTok{urlnorm}\NormalTok{(seasons, Rmu, Rsd_annual, }\DataTypeTok{lb =} \DecValTok{0}\NormalTok{, }\DataTypeTok{ub =} \DecValTok{200}\NormalTok{)}
  \NormalTok{\}}

@@

In the main text we constrained our focus to four-species communities
because getting more than four species to coexist by relative
nonlinearity is tricky, and usually requires adding another coexistence
mechanism on top of relative nonlinearity (Yuan \& Chesson 2015). The
storage effect does not suffer from this limitation, but we wanted our
results in the main text to be easily comparable between coexistence
mechanisms. Here, we show that our results are qualitatively similar if
we simulate an eight-species community with species coexistence
maintained by the storage effect. We conducted the same numerical
simulations described in the main text for Figure 2. Quoting from the
main text:

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{./components/SI_storage_effect_eightspp_local_regional.png}
  \caption{Variability of total community biomass as a function of species richness when coexistence is maintained by the storage effect. The left panel shows results from simulations where environmental cue variance determines the number of species that coexist in a community. The right panel shows results from simulations where environmental cue variance is fixed at a level ($\sigma_E^2=10$, which is where the far right cluster of points are in the left panel) that allows coexistence of all eight species, but species are removed to manipulate diversity. The left-hand panel represents a "regional" diversity--ecosystem variability relationship across a natural diversity gradient, whereas the right-hand panel represents a "local" diversity--ecosystem variability relationship. Points are jittered within discrete richness values for visual clarity. Lines show the mean trend (loess fits).}
\end{figure}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Environment-competition covariance (\emph{EC} covariance) becomes less
  positive
\item
  Environmental variation decreases
\item
  Buffering of population growth rate declines
\end{enumerate}

@@

Our results are qualitatively similar: (1) increasing environmental
variation allows more species to coexist, creating a positive
relationship between species richness and ecosystem variability
(richness increases along x-axes within panels); (2) and at any given
level of environmental variability, it is always better to have more
species, creating a within-site negative relationship between species
richness and ecosystem variability (Fig. SI-2). Although the qualitative
patterns are similar, increasing the dormant mortality rate has three
consistent effects: (1) it makes coexistence more difficult, (2) it
reduces the absolute value of ecosystem \emph{CV} by slightly reducing
mean population size and significantly reducing temporal standard
deviation, and (3) it weakens the buffering effect of additional species
(compare the spread of the lines between top and bottom panels of Fig.
SI-2). The second result occurs because population fluctuations are
reduced when very little biomass can be activated to the live stage at
the beginning of each season. That is, in terms of an annual plant,
germination of live biomass is always a fraction of a very small number.
The third result is a consequence of the second: populations are not
fluctuating that much, so total \emph{CV} can only be reduced by as much
with the addition of another species.

@@

Condition 1 is already included in our main analysis (Figures 2 and 4 in
the main text). Condition 2 simply creates conditions where some species
cannot coexist, which would not change the relationship between species
richness and ecosystem variability, but rather disallow it. Condition 3
could create situations where species may not coexist, but it could also
weaken the diversity--ecosystem variabilty relationship by reducing mean
biomass and the effect of species with very nonlinear growth rates. To
explore the effect of condition 3, we ran simulations across a gradient
of resource variability (11 levels) crossed with a gradient of mean
resource levels (4 levels: \(\mu_R = 1,2,3,4\)).

As expected, lower mean levels of resource make coexistence more
difficult because resource acquisitive species are never favored (Fig.
SI-3). Our general conclusion remains, however, that positive
diversity--ecosystem variability relationships are possible. However,
the occurrence of a positive diversity--ecosystem variability
relationship depends on the extent of the resource variability gradient
and the traits of individual species (e.g., resource uptake curves). In
other words, the patterns we report in the main text require that
fluctuation-dependent species coexistence be possible given the
environmental conditions and species' traits.

\begin{figure}[!ht]
  \centering
      \includegraphics[width=7in]{./components/SI_relative_nonlinearity_four_rmus.png}
  \caption{The effect of environmental variability on ecosystem variability when species coexist via relative nonlinearity. The species pool increases from one to four species, with the fourth species being most unstable (e.g., resource conservative to resource acquisitive). Increasing environmental variability (the SD of annual resource availability) allows for greater species richness, but species additions do not modulate the effect of environmental variability on ecosystem variability. Higher values of mean resource availability (left to right across panels) makes coexistence easier. Parameter values are as in Figure 2C in the main text.}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=5in]{./components/SI_big_sigE_gradient_extreme_events.png}
  \caption{The number of extreme germination events ($\gamma<0.01$) at different levels of germination cue variance($\sigma_E^2$). Past $\sigma_E^2=2$ the number of extreme germination events increases rapidly. This is why, in a four-species community, ecosystem \emph{CV} is flat up to $\sigma_E^2=2$ (as in Fig. 3A of the main text) but then begins to increase (Fig. SI-9). Because germination is bounded at 0 and 1, once germination begins to approah those values more frequently, the portfolio effects possible when species are perfectly anti-correlated can no longer perfectly compensate for increased population variability.}
\end{figure}

\begin{figure}[!ht]
  \centering
      \includegraphics[width=5in]{./components/SI_storage_effect_two_rmus_fourSpeciesOnly.png}
  \caption{Ecosystem \emph{CV} of a four-species community coexisting via the storage effect as a function of environmental cue variance at two levels of mean resource availability (\texttt{Rmu} across tops of panels) and two levels of correlation of species' responses to environmental conditions ($\rho$). Here we simulated community dynamics across a greater range of environmental cue variance (up to 10) to show that the \emph{CV} of four-species communities does not remain flat as environmental variance increases beyond levels shown in the main text. The mean resource level has no effect on the results.}
\end{figure}

### 2017-03-31 manuscript/coexistence-stability_ms.Rmd
final edits for R1 submission

\Large{The relationship between species richness and ecosystem variability is shaped by the mechanism of coexistence}

@@

We assume the resource pool is not replenished within a growing season.
Resource replenishment occurs between growing seasons, and the resource pool (*R*) at the start of the growing season is $R_{\tau(0)} = R^+$, where $R^+$ is a random resource pulse drawn from a log-normal distribution with mean $\mu(R^+)$ and standard deviation $\sigma(R^+)$. 
\new{Taken all together, we can combine equations 1 and 4 to define the discrete transitions between live and dormant biomass at the end of a growing season.
Thus, the initial conditions for each state ($D, N, R$) at the beginning of growing season $\tau+1$ are:}
\vspace{-3em}
\begin{align}
  D_{i,\tau(0) + 1} &= (1-\gamma_{i,\tau}) \left[\alpha_i N_{i,\tau(T)} + D_{i,\tau(T)} \right] (1-\eta_i) \\
  N_{i,\tau(0) + 1} &= \gamma_{i,\tau} \left[\alpha_i N_{i,\tau(T)} + D_{i,\tau(T)} \right] (1-\eta_i) \\
  R_{\tau(0) + 1} &= \text{lognormal}\left(\mu(R^+), \sigma(R^+) \right)_0^{200},
\end{align}
\vspace{-3em}
\noindent \new{where, as above, $\tau(T)$ denotes the end of growing season $\tau$ and $\tau(0) + 1$ denotes the beginning of growing season $\tau+1$.} 
\new{The subscript (0) and superscript (200) indicates a lognormal distribution truncated at those values.
We used the function \texttt{urlnorm} from the "Runuran" package} [@Leydold2015] \new{to generate values from the truncated lognormal distribution.}
Model parameters and notation are described in Table 1.

@@

To understand how increasing environmental variability will impact ecosystem variability when coexistence is fluctuation-dependent, we simulated the model over a range of species pool sizes and environmental cue or resource variability.
For each size of species pool (1, 2, 3, or 4 species), we simulated the model at 15 evenly-spaced levels of environmental cue (range = [0.1, 2]) for the storage effect and 25 evenly-spaced levels of resource variability (range = [0, 1.2]) for relative nonlinearity.
We also explored the influence of asymmetries in species' competitive abilities and correlations in species' environmental responses within the storage effect model.

@@

In communities where species coexist via relative nonlinearity, the extent to which species additions buffer ecosystem stability against increases in environmental variability depends on the species traits of immigrating species and the order in which they enter the community.
When additional species, which immigrate from the regional pool, are less intrinsically stable than the resident species, ecosystem variability increases at a relatively constant rate even as species are added (Fig. 4A; Fig. SI-11).
If more stable species colonize, species additions buffer the ecosystem from increasing environmental variability (Fig. 4B).

@@

\begin{table}[!htbp]
\caption{Default values of model parameters and their descriptions. Parameters that vary depending on the mode and strength of species coexistence or depending on species competitive hierarchies are labeled as ``variable'' in parentheses. The dormant-to-live biomass transition fraction ($\gamma$) is a function of other parameters, so has no default value.}
\begin{tabular}{l l l}
\hline
Parameter & Description & Value \\
\hline
$r$ & maximum per capita growth rate & 0.2 (variable) \\
$a$ & Hill function rate parameter & 2.0 (variable) \\
$b$ & Hill function curvature parameter & 2.5 (variable) \\
$\epsilon$ & resource-to-biomass conversion efficiency & 0.5 \\
$\alpha$ & allocation fraction of live biomass to dormant biomass & 0.5 (variable) \\
$\gamma$ & dormant-to-live biomass transition fraction & --- \\
$\rho$ & correlation of species' response to the environment & 0.0 (variable) \\
$\sigma_E$ & variance of the environmental cue & 2.0 (variable) \\
$\eta$ & dormant biomass mortality rate & 0.1 \\
$\mu(R^+)$ & mean annual resource pulse & 20 \\
$\sigma(R^+)$ & standard deviation of annual resource pulse & 0.0 (variable) \\
\hline
\end{tabular}
\end{table}

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[height=5in]{/Users/atredenn/Google_Drive/coexistence-stability_submission/figures/coex_stability_figure1.png}
  \caption{Variability of total community biomass as a function of species richness when coexistence is maintained by the storage effect (A,B) or relative nonlinearity (C,D). Left panels show results from simulations where environmental or resource variance determine the number species that coexist in a community. Right panels show results from simulations where environmental or resource variance is fixed at a level that allows coexistence of all four species, but species are removed to manipulate diversity. The left-hand panels represent ``regional'' diversity--ecosystem variability relationships across natural diversity gradients, whereas the right-hand panels represent ``local'' diversity--ecosystem variability relationships. Points are jittered within discrete richness values for visual clarity. Parameter values, where species are denoted by numeric subscripts: (A) $r_1 = r_2 = r_3 = r_4 = 0.2$, $a_1 = a_2 = a_3 = a_4 = 2$, $b_1 = b_2 = b_3 = b_4 = 2.5$, $\alpha_1 = 0.5, \alpha_2 = 0.49, \alpha_3 = 0.48, \alpha_4 = 0.47$, $\rho_1 = \rho_2 = \rho_3 = \rho_4 = 0$, $\sigma_E =$ variable; (B) $r_1 = r_2 = r_3 = r_4 = 0.2$, $a_1 = a_2 = a_3 = a_4 = 2$, $b_1 = b_2 = b_3 = b_4 = 2.5$, $\alpha_1 = 0.5, \alpha_2 = 0.49, \alpha_3 = 0.48, \alpha_4 = 0.47$, $\rho_1 = \rho_2 = \rho_3 = \rho_4 = -1/3$, $\sigma_E = 4$; (C) $r_1 = 0.2, r_2 = 1, r_3 = 2, r_4 = 5$, $a_1 = 2, a_2 = 5, a_3 = 10, a_4 = 25$, $b_1 = 2.5, b_2 = 20, b_3 = 30, b_4 = 45$, $\alpha_1 = \alpha_2 = \alpha_3 = \alpha_4 = 0.5$, $\rho_1 = \rho_2 = \rho_3 = \rho_4 = 1$, $\sigma(R^+) =$ variable; (D) $r_1 = 0.2, r_2 = 1, r_3 = 2, r_4 = 5$, $a_1 = 2, a_2 = 5, a_3 = 10, a_4 = 25$, $b_1 = 2.5, b_2 = 20, b_3 = 30, b_4 = 45$, $\alpha_1 = \alpha_2 = \alpha_3 = \alpha_4 = 0.5$, $\rho_1 = \rho_2 = \rho_3 = \rho_4 = 1$, $\sigma(R^+) =$ 1.1.}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[height=2.5in]{/Users/atredenn/Google_Drive/coexistence-stability_submission/figures/coex_stability_figure3.png}
  \caption{The effect of environmental variability on ecosystem variability when species coexist via relative nonlinearity. (A) The species pool increases from one to four species, with the fourth species being most unstable (e.g., resource conservative to resource acquisitive). Increasing environmental variability (the SD of annual resource availability) allows for greater species richness, but species additions do not modulate the effect of environmental variability on ecosystem variability. (B) The species pool increases from one to four species, with the fourth species being most stable (e.g., resource acquisitive to resrouce conservative). In this case, increasing environmental variability allows for greater realized species richness and can temper the effect of environmental variability. Parameter values are as in Figure 2C.}
\end{figure}

>>>>

\Large{\textbf{The relationship between species richness and ecosystem variability is shaped by the mechanism of coexistence}}

@@

We assume the resource pool is not replenished within a growing season.
Resource replenishment occurs between growing seasons, and the resource pool (*R*) at the start of the growing season is $R_{\tau(0)} = R^+$, where $R^+$ is a random resource pulse drawn from a lognormal distribution with mean $\mu(R^+)$ and standard deviation $\sigma(R^+)$. 
\new{Taken all together, we can combine equations 1 and 4 to define the discrete transitions between live and dormant biomass at the end of a growing season.
Thus, the initial conditions for each state ($D, N, R$) at the beginning of growing season $\tau+1$ are:}
\vspace{-3em}
\begin{align}
  D_{i,\tau(0) + 1} &= (1-\gamma_{i,\tau}) \left[\alpha_i N_{i,\tau(T)} + D_{i,\tau(T)} \right] (1-\eta_i) \\
  N_{i,\tau(0) + 1} &= \gamma_{i,\tau} \left[\alpha_i N_{i,\tau(T)} + D_{i,\tau(T)} \right] (1-\eta_i) \\
  R_{\tau(0) + 1} &= \text{lognormal}\left(\mu(R^+), \sigma(R^+) \right)_0^{200},
\end{align}
\vspace{-3em}
\noindent \new{where, as above, $\tau(T)$ denotes the end of growing season $\tau$ and $\tau(0) + 1$ denotes the beginning of growing season $\tau+1$.} 
\new{The subscript (0) and superscript (200) indicates a lognormal distribution truncated at those values to avoid extreme resource pulses that cause computational problems.
We used the function \texttt{urlnorm} from the \texttt{Runuran} package} [@Leydold2015] \new{to generate values from the truncated lognormal distribution.}
Model parameters and notation are described in Table 1.

@@

To understand how increasing environmental variability will impact ecosystem variability when coexistence is fluctuation-dependent, we simulated the model over a range of species pool sizes and environmental cue or resource variability.
For each size of species pool (1, 2, 3, or 4 species), we simulated the model at 15 evenly-spaced levels of environmental cue (range = [0.1, 2]) for the storage effect and 25 evenly-spaced levels of resource variability (range = [0, 1.2]) for relative nonlinearity.
We also explored the influence of asymmetries in species' competitive abilities and correlations in species' environmental responses within the storage effect model.
\new{We created competitive hierarchies by making the live-to-dormant biomass fractions ($\alpha$s) unequal among species.
A small difference among values of $\alpha$ were needed to create competitive hierarchies because we chose a relatively constrained gradient of environmental cue variance.
Larger differences among values of $\alpha$ expand the region of coexistence farther along a gradient environmental cue variance.
These parameter value choices do not affect our conclusions, but would change the quantitative results.}

@@

In communities where species coexist via relative nonlinearity, the extent to which species additions buffer ecosystem stability against increases in environmental variability depends on the species traits of immigrating species and the order in which they enter the community.
When additional species, which immigrate from the regional pool, are less intrinsically stable than the resident species, ecosystem variability increases at a relatively constant rate even as species are added (Fig. 4A; Fig. SI-11).
If more stable species colonize, species additions buffer the ecosystem from increasing environmental variability (Fig. 4B).
\new{The "stair-steps" in Fig. 4B emerge because a different species is making up the one-species community at different levels of resource variability, increasing ecosystem \emph{CV} each time as a more unstable species composes the single species community.}

@@

\begin{table}[!htbp]
\caption{Default values of model parameters and their descriptions. Parameters that vary depending on the mode and strength of species coexistence or depending on species competitive hierarchies are labeled as ``variable'' in parentheses. The dormant-to-live biomass transition fraction ($\gamma$) is a function of other parameters, so has no default value.}
\begin{tabular}{l l l}
\hline
Parameter & Description & Value \\
\hline
$r$ & maximum per capita growth rate & 0.2 (variable) \\
$a$ & Hill function curvature parameter & 2.0 (variable) \\
$b$ & Hill function scale parameter & 2.5 (variable) \\
$\epsilon$ & resource-to-biomass conversion efficiency & 0.5 \\
$\alpha$ & allocation fraction of live biomass to dormant biomass & 0.5 (variable) \\
$\gamma$ & dormant-to-live biomass transition fraction & --- \\
$\rho$ & correlation of species' response to the environment & 0.0 (variable) \\
$\sigma_E$ & variance of the environmental cue & 2.0 (variable) \\
$\eta$ & dormant biomass mortality rate & 0.1 \\
$\mu(R^+)$ & mean annual resource pulse & 20 \\
$\sigma(R^+)$ & standard deviation of annual resource pulse & 0.0 (variable) \\
\hline
\end{tabular}
\end{table}

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[height=5in]{/Users/atredenn/Google_Drive/coexistence-stability_submission/figures/coex_stability_figure1.png}
  \caption{Variability of total community biomass as a function of species richness when coexistence is maintained by the storage effect (A,B) or relative nonlinearity (C,D). Left panels show results from simulations where environmental or resource variance determine the number species that coexist in a community. Right panels show results from simulations where environmental or resource variance is fixed at a level that allows coexistence of all four species, but species are removed to manipulate diversity. The left-hand panels represent ``regional'' diversity--ecosystem variability relationships across natural diversity gradients, whereas the right-hand panels represent ``local'' diversity--ecosystem variability relationships. \new{Note that we do not attribute any particular area size to "region", it is simply any area over which a gradient of environmental variability can emerge.} Points are jittered within discrete richness values for visual clarity. Parameter values, where species are denoted by numeric subscripts: (A) $r_1 = r_2 = r_3 = r_4 = 0.2$, $a_1 = a_2 = a_3 = a_4 = 2$, $b_1 = b_2 = b_3 = b_4 = 2.5$, $\alpha_1 = 0.5, \alpha_2 = 0.49, \alpha_3 = 0.48, \alpha_4 = 0.47$, $\rho_1 = \rho_2 = \rho_3 = \rho_4 = 0$, $\sigma_E =$ variable; (B) $r_1 = r_2 = r_3 = r_4 = 0.2$, $a_1 = a_2 = a_3 = a_4 = 2$, $b_1 = b_2 = b_3 = b_4 = 2.5$, $\alpha_1 = 0.5, \alpha_2 = 0.49, \alpha_3 = 0.48, \alpha_4 = 0.47$, $\rho_1 = \rho_2 = \rho_3 = \rho_4 = -1/3$, $\sigma_E = 4$; (C) $r_1 = 0.2, r_2 = 1, r_3 = 2, r_4 = 5$, $a_1 = 2, a_2 = 5, a_3 = 10, a_4 = 25$, $b_1 = 2.5, b_2 = 20, b_3 = 30, b_4 = 45$, $\alpha_1 = \alpha_2 = \alpha_3 = \alpha_4 = 0.5$, $\rho_1 = \rho_2 = \rho_3 = \rho_4 = 1$, $\sigma(R^+) =$ variable; (D) $r_1 = 0.2, r_2 = 1, r_3 = 2, r_4 = 5$, $a_1 = 2, a_2 = 5, a_3 = 10, a_4 = 25$, $b_1 = 2.5, b_2 = 20, b_3 = 30, b_4 = 45$, $\alpha_1 = \alpha_2 = \alpha_3 = \alpha_4 = 0.5$, $\rho_1 = \rho_2 = \rho_3 = \rho_4 = 1$, $\sigma(R^+) =$ 1.1.}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[height=2.5in]{/Users/atredenn/Google_Drive/coexistence-stability_submission/figures/coex_stability_figure3.png}
  \caption{The effect of environmental variability on ecosystem variability when species coexist via relative nonlinearity. (A) The species pool increases from one to four species, with the fourth species being most unstable (e.g., resource conservative to resource acquisitive). Increasing environmental variability (the SD of annual resource availability) allows for greater species richness, but species additions do not modulate the effect of environmental variability on ecosystem variability. (B) The species pool increases from one to four species, with the fourth species being most stable (e.g., resource acquisitive to resource conservative). In this case, increasing environmental variability allows for greater realized species richness and can temper the effect of environmental variability. Parameter values are as in Figure 2C.}
\end{figure}

### 2017-03-31 manuscript/coexistence-stability_ms.tex
final edits for R1 submission

We assume the resource pool is not replenished within a growing season.
Resource replenishment occurs between growing seasons, and the resource
pool (\emph{R}) at the start of the growing season is
\(R_{\tau(0)} = R^+\), where \(R^+\) is a random resource pulse drawn
from a log-normal distribution with mean \(\mu(R^+)\) and standard
deviation \(\sigma(R^+)\).
\new{Taken all together, we can combine equations 1 and 4 to define the discrete transitions between live and dormant biomass at the end of a growing season.
Thus, the initial conditions for each state ($D, N, R$) at the beginning of growing season $\tau+1$ are:}
\vspace{-3em}

@@

\noindent \new{where, as above, $\tau(T)$ denotes the end of growing season $\tau$ and $\tau(0) + 1$ denotes the beginning of growing season $\tau+1$.}
\new{The subscript (0) and superscript (200) indicates a lognormal distribution truncated at those values.
We used the function \texttt{urlnorm} from the "Runuran" package}
(Leydold \& Hörmann 2015)
\new{to generate values from the truncated lognormal distribution.}
Model parameters and notation are described in Table 1.

@@

To understand how increasing environmental variability will impact
ecosystem variability when coexistence is fluctuation-dependent, we
simulated the model over a range of species pool sizes and environmental
cue or resource variability. For each size of species pool (1, 2, 3, or
4 species), we simulated the model at 15 evenly-spaced levels of
environmental cue (range = {[}0.1, 2{]}) for the storage effect and 25
evenly-spaced levels of resource variability (range = {[}0, 1.2{]}) for
relative nonlinearity. We also explored the influence of asymmetries in
species' competitive abilities and correlations in species'
environmental responses within the storage effect model.

>>>>

We assume the resource pool is not replenished within a growing season.
Resource replenishment occurs between growing seasons, and the resource
pool (\emph{R}) at the start of the growing season is
\(R_{\tau(0)} = R^+\), where \(R^+\) is a random resource pulse drawn
from a lognormal distribution with mean \(\mu(R^+)\) and standard
deviation \(\sigma(R^+)\).
\new{Taken all together, we can combine equations 1 and 4 to define the discrete transitions between live and dormant biomass at the end of a growing season.
Thus, the initial conditions for each state ($D, N, R$) at the beginning of growing season $\tau+1$ are:}
\vspace{-3em}

@@

\noindent \new{where, as above, $\tau(T)$ denotes the end of growing season $\tau$ and $\tau(0) + 1$ denotes the beginning of growing season $\tau+1$.}
\new{The subscript (0) and superscript (200) indicates a lognormal distribution truncated at those values to avoid extreme resource pulses that cause computational problems.
We used the function \texttt{urlnorm} from the \texttt{Runuran} package}
(Leydold \& Hörmann 2015)
\new{to generate values from the truncated lognormal distribution.}
Model parameters and notation are described in Table 1.

@@

To understand how increasing environmental variability will impact
ecosystem variability when coexistence is fluctuation-dependent, we
simulated the model over a range of species pool sizes and environmental
cue or resource variability. For each size of species pool (1, 2, 3, or
4 species), we simulated the model at 15 evenly-spaced levels of
environmental cue (range = {[}0.1, 2{]}) for the storage effect and 25
evenly-spaced levels of resource variability (range = {[}0, 1.2{]}) for
relative nonlinearity. We also explored the influence of asymmetries in
species' competitive abilities and correlations in species'
environmental responses within the storage effect model.
\new{We created competitive hierarchies by making the live-to-dormant biomass fractions ($\alpha$s) unequal among species.
A small difference among values of $\alpha$ were needed to create competitive hierarchies because we chose a relatively constrained gradient of environmental cue variance.
Larger differences among values of $\alpha$ expand the region of coexistence farther along a gradient environmental cue variance.
These parameter value choices do not affect our conclusions, but would change the quantitative results.}
